Self-test prime dimensional EPR pairs with constant alphabet

### 2019-04-02 Draft/draft.tex
Honghao: added the statistical distance measure and justifications, also refined the ideal strategy.

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
The goal of this section and the following two sections is to 
present a correlation that can self-test $\ket{\EPR{d-1}}$, 
where $d$ is prime and has primitive root $r \in \{2, 3, 5\}$,
and this correlation is denoted by $C(\dr{r})$.  \carl{Be more precise --- we are constructing
such a correlation for any $d$ which has $2, 3,$ or $5$ as a primitive root.}
The correlation we constructed is the optimal correlation for a game $\G(\dr{r})$, which is the combination of two tests.
In this section, we introduce the linear system game which tests a relation that should be satisfied by 
Alice and Bob's observables.

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.  \carl{That sentence
is too vague -- either make it a rigorous statement or leave it out.}
The main component of $\G(\dr{r})$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg_r= \langle u, x : uxu^{-1} = x^r \rangle, \text{ for } r \in \{2, 3,5\}.
\end{align}
In other words, relations in the presentation of the solution group of $\LS_r$ can be combined to derive the
relation $uxu^{-1} = x^r$.  
\begin{proposition}
	\label{prop:embed}
	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
	with constant numbers of variables and equations, where each equation involves $3$ variables.
	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
	that the numbers of variables and equations is independent of $r$, which I'm pretty sure is not true.)}
\end{proposition}
The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Ref.~\cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
and \cref{sec:power5} for $r = 5$.

@@

\textbf{The ideal strategy for the weighted $\CHSH_X$ test}.
Alice and Bob share state $\ket{\psi} = \frac{1}{\sqrt{d-1}}\sum_{i=1}^{d-1} \ket{ii}$ and choose the special subspace to be 
$V = \spn(\ket{1} ,\ket{d-1})$.
Alice's projectors and observables for the weighted $\CHSH_X$ test are
\begin{align*}
	&A_0^\diamond = \ketbra{1}{1} + \ketbra{d-1}{d-1}, &&A_0^\perp = \1 - A_\ast^\diamond, \\
	&A_{m_r+2} = A_{m_r+2}^0-A_{m_r+2}^1 = \ketbra{1}{1} - \ketbra{d-1}{d-1}, &&A_{m_r+2}^\perp = A_\ast^\perp,\\
	&A_{m_r+3} = A_{m_r+3}^0-A_{m_r+3}^1 = \ketbra{1}{d-1} + \ketbra{d-1}{1} ,&&A_{m_r+3}^\perp = A_\ast^\perp.
\end{align*}
Recall that in the extended weighted $\CHSH_X$ test, what matters is the 
Bob's observables restricted to the subspace $V$, which are given by
\begin{align*}
	B_1|_V = \cos(\frac{\pi}{d})(\ketbra{1}{1} - \ketbra{d-1}{d-1}) - \sin(\frac{\pi}{d})(\ketbra{1}{d-1} + \ketbra{d-1}{1}),\\
	B_2|_V = \cos(\frac{\pi}{d})(\ketbra{1}{1} - \ketbra{d-1}{d-1}) +\sin(\frac{\pi}{d})(\ketbra{1}{d-1} + \ketbra{d-1}{1}).
\end{align*}
To make sure operator $B_2$ commutes with the operator $U = \Psi(x_3x_4) = \Psi(u)$ that we will construct later, we pick a 
special basis of $X|_V =B_1|_VB_2|_V$, which is
\begin{align}
	\ket{x_1} = \frac{-1}{\sqrt{2}}(\ket{1} + i\ket{d-1}), &&
	\ket{x_{d-1}} = \frac{-e^{i\pi/d}}{\sqrt{2}}(\ket{1} - i\ket{d-1}).
\end{align}
It can be checked that $X\ket{x_1} = \omega_d \ket{x_1}$ and $X\ket{x_{d-1}} = \omega_d^{d-1} \ket{x_{d-1}}$.
In this basis, $B_1|_V$ and $B_2|_V$ are expressed as 
\begin{align}
	&B_1|_V = \omega_d\ketbra{x_1}{x_{d-1}} + \omega_d^{-1} \ketbra{x_{d-1}}{x_1},\\
	&B_2|_V =\ketbra{x_1}{x_{d-1}}  + \ketbra{x_{d-1}}{x_1}.
\end{align}
\hl{If we express $\ket{j}$'s as $\ket{x_j}$'s, then we can find that 
shared state is}\\
\hl{ $\sum_{j=1}^{d-1} \ket{j}\ket{j} = \sum_{j=0}^{(d-1)/2} e^{-ij\pi/d} (\ket{x_{j}}\ket{x_{d-j}} + \ket{x_{d-j}}\ket{x_{j}}$.}

>>>>

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
The goal of this section and the following two sections is to 
present a correlation that can self-test $\ket{\EPR{d-1}}$, 
where $d$ is prime with primitive root $r$,
and this correlation is denoted by $C(\dr{r})$.  \carl{Be more precise --- we are constructing
such a correlation for any $d$ which has $2, 3,$ or $5$ as a primitive root.}
\hf{One part of $C(\dr{r})$ is produced by the optimal quantum strategy of a linear system game, denoted by $\LS$.}
In this section, we introduce the linear system game which tests a key relation that should be satisfied by 
Alice and Bob's observables.

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.  \carl{That sentence
is too vague -- either make it a rigorous statement or leave it out.}
\hf{We generalize this relation and make he solution group of $\LS$ the embedding of the 
following group}
\begin{align}
	\Pg_r= \langle u, o : uou^{-1} = o^r \rangle, \text{ for } r \in \N.
\end{align}
In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
relation $uou^{-1} = o^r$.  
\begin{proposition}
	\label{prop:embed}
	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
	with the numbers of variables and equations linear in $r$, where each equation involves $3$ variables.
	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
	that the numbers of variables and equations is independent of $r$, which I'm pretty sure is not true.)}
\end{proposition}
The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Ref.~\cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
and \cref{sec:power5} for $r = 5$.

@@

\textbf{The ideal strategy for the weighted $\CHSH_X$ test}.
Alice and Bob share state 
\begin{align}
	\ket{\psi} = \frac{1}{\sqrt{d-1}}\sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})
\end{align}	
and choose the special subspace to be 
$V = \spn(\ket{1} ,\ket{d-1})$.
Alice's projectors and observables for the weighted $\CHSH_X$ test are
\begin{align*}
	&A_0^\diamond = \ketbra{1}{1} + \ketbra{d-1}{d-1}, &&A_0^\perp = \1 - A_\ast^\diamond, \\
	&A_{m_r+2} = A_{m_r+2}^0-A_{m_r+2}^1 = \ketbra{1}{1} - \ketbra{d-1}{d-1}, &&A_{m_r+2}^\perp = A_\ast^\perp,\\
	&A_{m_r+3} = A_{m_r+3}^0-A_{m_r+3}^1 = \ketbra{1}{d-1} + \ketbra{d-1}{1} ,&&A_{m_r+3}^\perp = A_\ast^\perp.
\end{align*}
Recall that in the extended weighted $\CHSH_X$ test, what matters is the 
Bob's observables restricted to the subspace $V$, which are given by
\begin{align*}
	B_1|_V = \cos(\frac{\pi}{d})(\ketbra{1}{1} - \ketbra{d-1}{d-1}) - \sin(\frac{\pi}{d})(\ketbra{1}{d-1} + \ketbra{d-1}{1}),\\
	B_2|_V = \cos(\frac{\pi}{d})(\ketbra{1}{1} - \ketbra{d-1}{d-1}) +\sin(\frac{\pi}{d})(\ketbra{1}{d-1} + \ketbra{d-1}{1}).
\end{align*}
To make sure operator $B_2$ commutes with the operator $U = \Psi(x_3x_4) = \Psi(u)$ that we will construct later, we pick a 
special basis of $X|_V =B_1|_VB_2|_V$, which is
\begin{align}
	\ket{x_1} = \frac{-1}{\sqrt{2}}(\ket{1} + i\ket{d-1}), &&
	\ket{x_{d-1}} = \frac{-e^{i\pi/d}}{\sqrt{2}}(\ket{1} - i\ket{d-1}).
\end{align}
It can be checked that $X\ket{x_1} = \omega_d \ket{x_1}$ and $X\ket{x_{d-1}} = \omega_d^{d-1} \ket{x_{d-1}}$.
In this basis, $B_1|_V$ and $B_2|_V$ are expressed as 
\begin{align}
	&B_1|_V = \omega_d\ketbra{x_1}{x_{d-1}} + \omega_d^{-1} \ketbra{x_{d-1}}{x_1},\\
	&B_2|_V =\ketbra{x_1}{x_{d-1}}  + \ketbra{x_{d-1}}{x_1}.
\end{align}
Extending $B_1|_V$ and $B_2|_V$ to the whole space spanned by $\{ \ket{j} \}_{j=1}^{d-1}$ gives us that
\begin{align}
	B_1 =\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}} &&
	B_2 = \sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}},
\end{align}
where the basis state $\ket{x_j}$ and $\ket{x_{d-j}}$ are defined by
\begin{align}
	\ket{x_j} = \frac{-1}{\sqrt{2}}(\ket{j} + i\ket{d-j}), &&
	\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j}) \text{ for } j = 1 \dots \frac{d-1}{2}.
\end{align}
If we use the basis $\{ \ket{x_j} \}_{j=1}^{d-1}$, the shared state is 
\begin{align}
	\ket{\psi} =& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\\
	=& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{(d-1)/2}  e^{ij\pi/d}e^{-ij\pi/d} (\ket{x_{j}}\ket{x_{d-j}} + \ket{x_{d-j}}\ket{x_{j}} \\
	=& \frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j} \ket{x_{d-j}}.
\end{align}
